Concurrent Programming in Harmony

### 2021-04-18 book/paper.tex
Latest

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{figures/queuefix1.pdf}
\end{center}
\caption{Harmony output.}
\label{fig:queuefix1}
\end{figure}

@@

\autoref{fig:queuefix1} shows the Harmony output of running
the test in \autoref{fig:qtest3} against the queue code
in \autoref{fig:queuebug}.
There is quite a bit of information in the Harmony output, and it's
important to learn to navigate through it.
Let's start with looking at the red text.  Harmony found a safety
violation (something bad happened during one of the possible executions),
and in particular \texttt{putter}(1) (thread T2) was trying to dereference
\texttt{alloc}.\textit{pool}[0].\texttt{lock} in turn 5.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\textwidth]{figures/queuebug1.pdf}
\end{center}
\caption{Harmony output of running \autoref{fig:qtest3} against
\autoref{fig:queuebug}.}
\label{fig:queuebug1}
\end{figure}

@@

\autoref{fig:queuebug1} shows the Harmony output of running
the test in \autoref{fig:qtest3} against the queue code
in \autoref{fig:queuebug}.
There is quite a bit of information in the Harmony output, and it's
important to learn to navigate through it.
Let's start with looking at the red text.  Harmony found a safety
violation (something bad happened during one of the possible executions),
and in particular \texttt{putter}(1) (thread T2) was trying to dereference
\texttt{alloc}.\textit{pool}[0].\texttt{lock} in turn 5.
